---
title: "Boots_OriginalCode_brennas"
author: "brennastallings"
date: "11/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is for [Homework 5](https://fuzzyatelin.github.io/bioanth-stats/homework-05.html)

Comentary: You can use the packages simple boot and boot to run your boostrap and calculate CIs. These packages will make life much easier. 

First we call any libraries we need
```{r}
library(ggplot2)
library(curl)
library(lmodel2)
library(dplyr)
```
Then we call in the data set needed
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
The we start the fun

>[1] 

#Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
```{r}
m<- lm(log(HomeRange_km2)~log(Body_mass_female_mean), data=d)
m
```
β0=-9.441
β1=1.036

>[2] 

#Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
```{r}
samp_b0<- NULL
samp_b1<- NULL
n<- 50
for (i in 1:1000){
  d[i]<- sample_n(d, n, replace=T)
  m[i]<- lm(log(HomeRange_km2)~log(Body_mass_female_mean), data=d[i])
  samp_b0[i]<-m[i]$coefficients[1]
  samp_b1[i]<-m[i]$coefficients[2]
}

```
This isnt working at the moment, I googled the error and it didnt help. It works if I do each by hand, but cant add to samp
I made a sample set to test math with
```{r}
samp.test<- rbind(samp1, samp2)
```


#Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap 
```{r}
sd(samp_b0)
sd(samp_b1)
```
test code
```{r echo=F}
#this is for 'b0'
sd(samp.test[,1])
#this is for 'b1'
sd(samp.test[,2])
```


#Determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
```{r}
ci<-
```
test code
```{r}
t <- c(mean(samp.test[,1]), sd(samp.test[,1]), (mean(samp.test[,1])/sd(samp.test[,1])))
t1<- c(mean(samp.test[,2]), sd(samp.test[,2]), (mean(samp.test[,2])/sd(samp.test[,2])))
t<- rbind(t, t1)
colnames(t) <- c("Est", "SE","t")
t<- as.data.frame(t)
t$lower <- t$Est - qt(0.975, df = 998) * t$SE
t$upper <- t$Est + qt(0.975, df = 998) * t$SE
ci <- c(t$lower, t$upper)  # by hand
ci
```


#How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
For the entire dataset:
```{r echo=F}
summary(m)
```
B0=0.672
B1=0.084
#How does the latter compare to the 95% CI estimated from your entire dataset?
Entire Dataset:
```{r}
ci <- confint(m, level = 0.95)  # using the results of lm()
ci
```
#Ill compare when I get working code.....

>5 Challenges

1.Obviously I have serious issues with my For Loop
</br>
2.
</br>
3.
</br>
4.
</br>
5.